---
title: "conditional_loops"
author: "Kiran Favre"
date: "2022-08-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Part 1

### Task 1

```{r}
pm2_5 <- 160
if (pm2_5 < 100) {
  print("Low to moderate risk")
} else if ( 100 <= pm2_5 & pm2_5 < 150){
  print("unhealthy for sensitive groups")
} else {(pm2_5>=150)
  print("health risk present")
}
```

### Task 2

```{r}
species <- "blue whale"
if (str_detect(species, "whale")){
  print("You found a whale!")}
```

### Task 3

```{r}
max_airtemp_C <- c(24.1)

if(max_airtemp_C > 27) {
  print("Temperature too high")
} else
  print("Temperature OK")
```

#### Task 4

```{r}
base_burrito <- 6.50
main_ingredient <- c("beef")
switch(main_ingredient,
       "veggie" = print(base_burrito),
       "chicken" = print(base_burrito +3),
       "beef" = print(base_burrito +3.50))

```

## For loops

### Task 5

##### Create a new vector called `fish` that contains the values `8, 10, 12, 23` representing counts of different fish types in a fish tank (goldfish, tetras, guppies, and mollies, respectively). Write a for loop that iterates through `fish`, and returns what proportion of total fish in the tank are that species. Assume that these counts represent all fish in the tank.

```{r}
fishproportions <- vector(mode = "numeric", length=length(types))

fish <- c(8, 10, 12, 23)
total_count <- sum(fish)
types<- c("goldfish", "tetras", "guppies", "mollies")

for (i in seq_along(fish)) {
 if (types[i] == "goldfish"){
   fish_prop <- fish[i]/total_count}
else if(types[i] == "tetras"){
  fish_prop <- fish[i]/total_count}
else if(types[i] == "guppies"){
  fish_prop <- fish[i]/total_count}
else if(types[i] == "mollies"){
  fish_prop <- fish[i]/total_count}
fishproportions[i] <- fish_prop
}

```

#### Task 6

```{r}
month_names <- month.name


for (i in seq_along(month_names)) {
  print(paste(month_names[i], "is month", i))
}
```
